\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-19 jss/article.tex
change

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data. Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law. Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage in (3) and Adam's and Eve's laws are taking conditional expectation and variance over them given data.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters. To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this Beta distribution.

@@

First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset. Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice properties. And it is the simplest one to estimate their true batting averages. But can we say this is the best way to predict their batting averages?
\\

@@

The meaning of putting the \code{gbo} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets. 
\\

>>>>

Once we estimate these two moments of shrinkage, we can also estimate the posterior moments given only data. Taking the Normal model as an example,  $E(\mu_{j}\vert \textbf{y})=E(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Adam's law and $Var(\mu_{j}\vert \textbf{y})=E(Var(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})+Var(E(\mu_{j}\vert \textbf{y}, r, A)\vert \textbf{y})$ by Eve's law. Note that both $E(\mu_{j}\vert \textbf{y}, r, A)$ and $Var(\mu_{j}\vert \textbf{y}, r, A)$ are a function of shrinkage (see (3)) and Adam's and Eve's laws are taking conditional expectation and variance over them given data, $\textbf{y}$. Since we have already estimated $E(B_{j}\vert\textbf{y})$ and $Var(B_{j}\vert\textbf{y})$ via ADM, fianlly we can estimate $E(\mu_{j}\vert \textbf{y})$ and $Var(\mu_{j}\vert \textbf{y})$.

\subsection[Approximation to Posterior Distribution by Moment Matching]{Approximation to Posterior Distribution via Matching Moments}
After estimating two posterior moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$ for the Binomial model, \code{gbp} reasonably approximates a posterior distribution given data, \emph{i.e.}, $p_{j}\vert \textbf{z}$ (or $\mu_{j}\vert \textbf{y}$, $\lambda_{j}\vert \textbf{z}$), by matching these two moments with its parameters. To be specific, we assumed $p_{j}\vert \textbf{z}$ had another Beta($a_{1}$, $a_{0}$) distribution and matched two estimated moments, $E(p_{j}\vert \textbf{z})$ and $Var(p_{j}\vert \textbf{z})$, with two parameters, $a_{1}$ and $a_{0}$, of this assumed Beta distribution.

@@

First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset. Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice asymptotic properties. And it is the simplest one to estimate their true batting averages. But can we say this is the best way to predict their batting averages?
\\

@@

The meaning of putting the \code{gbp} object, \code{b}, without any additional argument in the above \code{coverage} function is to make this function regard the estimated values, such as $\hat{r}$ (=112.95) and $\hat{\beta}~(=(-1.194, ~0.389)^{T})$, as true values for generating pseudo-datasets. 
\\
